Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
shortended formula

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}}$.

@@

	Next, we sum up all costs incurred by \OPT.
	By definitions of $R_t$ and $R^*_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,w\}}$ or
	$R_{t'} \cap R^*_{\{u,v\}} = \sigma_{\{u,w\}}$
	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\OPT ( \sigma_{\{u,w\}})$
	is counted at most twice in each of  the expressions
	$\OPT (R_{t'}) + \OPT (R_t)$
	and  
	$\OPT (R_{t'}) + \OPT(R^*_{\{u,v\}})$.
	Hence,
	for all collocations performed by \RM,
	and for final requests at $t=m$,
	\OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in T } \OPT (R_t) +
	\sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
	) $.
	Then,
	the total cost to \OPT is

	\begin{align*} 	%\label{eq:costOPT}
		\OPT (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \OPT (R_t) 
		+ \sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
		\Big)	\\
		&\geq
		\Big(
		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
		\Big)		
		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big),
	\end{align*}
and
$
	\RM(\sigma)	/
	\OPT (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big) 	\leq 6.
$
\end{proof}

\maciek{OPT's font differ from other proofs. We don't want italic OPT in mathenv}

\maciek{I really think that minimums should be expanded earlier than in the competitive ratio. The ratio should be bounded easily, and if you wish, you can emphasize the choice in the paragraph, or dedicate entire line to the cost expression. }

>>>>

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}} = \alpha$.

@@

	Next, we sum up all costs incurred by \OPT.
	By definitions of $R_t$ and $R^*_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,w\}}$ or
	$R_{t'} \cap R^*_{\{u,v\}} = \sigma_{\{u,w\}}$
	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\OPT ( \sigma_{\{u,w\}})$
	is counted at most twice in each of  the expressions
	$\OPT (R_{t'}) + \OPT (R_t)$
	and  
	$\OPT (R_{t'}) + \OPT(R^*_{\{u,v\}})$.
	Hence,
	for all collocations performed by \RM,
	and for final requests at $t=m$,
	\OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in T } \OPT (R_t) +
	\sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
	) $.
	Then,
	the total cost to \OPT is
	\begin{align*} 	%\label{eq:costOPT}
		\OPT (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \OPT (R_t) 
		+ \sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
		\Big)	
		\geq
%		\Big(
%		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
%		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
%		\Big)		
%		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big),
	\end{align*}
and
$
	\RM(\sigma)	/
	\OPT (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big) 	\leq 6.
$
\end{proof}
